---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = '#>',
  fig.path = 'man/figures/README-',
  out.width = '100%'
)
```

# wf

<!-- badges: start -->
<!-- badges: end -->

`wf` manages skills for AI coding agents.
Skills are reusable instruction sets that extend what an agent can do.
They live in a conventional directory for each agent (e.g., `.claude/skills/` for Claude Code) and can be installed from GitHub or a local path.

## Installation

```r
# install.packages('pak')
pak::pak('christopherkenny/wf')
```

## Setup

Set `WF_AGENT` in your `.Renviron` so every `wf` function knows which agent you use:

```r
usethis::edit_r_environ()
```

Add a line like:

```r
WF_AGENT='claude_code'
```

Supported agents: `'claude_code'` (alias: `'claude'`), `'openclaw'`, `'codex'`, `'cursor'`, `'gemini_cli'`, `'github_copilot'`.

Skills can be scoped to a project (`.agent/skills/`) or installed globally (`~/.agent/skills/`):

```{r skill_path}
library(wf)

skill_path('claude_code', 'project') # project-local
skill_path('claude_code', 'global') # user-global
skill_path() # auto-detected from WF_AGENT or directory
```

## Example

Install a skill from GitHub using its `owner/repo` shorthand or a full URL:

```r
add_skill('some-user/some-skill')
```

For repos that bundle multiple skills, use the `skill` argument:

```r
add_skill('some-user/skills', skill = 'proofread')
```

List, check, and update installed skills:

```{r skill_operations}
list_skills()
check_skills()
update_skills()
```

## Finding and creating skills

Search GitHub for community skills tagged with `claude-skill`:

```r
find_skill()               # all skills
find_skill('quarto')   # filtered by keyword
```

Scaffold a new skill with a template `SKILL.md`:

```{r init_skill}
tmp <- tempfile()
init_skill('my-skill', tmp)
```
