---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = '#>',
  fig.path = 'man/figures/README-',
  out.width = '100%'
)
```

# wf

<!-- badges: start -->
<!-- badges: end -->

`wf` is an R package for managing AI coding agent **skills**.
Skills are reusable instruction sets that extend what agents, like Claude Code, can do in your projects.

A skill is a directory containing a `SKILL.md` file with YAML frontmatter and markdown instructions.
Skills live in a conventional location for each agent (e.g., `.claude/skills/` for Claude Code) and can be shared, version controlled, and discovered on GitHub.

## Installation

```r
# install.packages('pak')
pak::pak('christopherkenny/wf')
```

## Getting started

### Tell `wf` which agent you use

Most users work with a single agent. Set `WF_AGENT` in your `.Renviron` once
and every `wf` function will pick it up automatically:

```r
usethis::edit_r_environ()
```

Then add:

```r
WF_AGENT='claude_code'
```

Supported agents: `'claude_code'` (alias: `'claude'`), `'openclaw'`, `'codex'`, `'cursor'`, `'gemini_cli'`, `'github_copilot'`.

If `WF_AGENT` is not set, wf scans the current directory for a recognized agent config folder (`.claude`, `.cursor`, etc.) and falls back to `'claude_code'` if none is found.

### Find the skills directory for your agent

```{r skill_path}
library(wf)

skill_path('claude_code', 'project') # project-local
skill_path('claude_code', 'global') # user-global
skill_path() # auto-detected from WF_AGENT or directory
```

## Installing skills

Install a skill from GitHub using its `owner/repo` shorthand or a full URL:

```r
add_skill('some-user/some-skill', skill_path())
```

Install from a local directory (useful for skills you are developing):

```r
add_skill('path/to/my-skill', skill_path())
```

## Listing installed skills

```{r list_skills}
list_skills(skill_path('claude_code', 'project'))
```

## Checking for updates

```{r check_skills}
check_skills(skill_path('claude_code', 'project'))
```

## Updating skills

```r
update_skills(skill_path())
```

## Removing a skill

```r
remove_skill('skill-name', skill_path(), force = TRUE)
```

## Finding skills on GitHub

Repositories tagged with the `claude-skill` topic are discoverable via
`find_skill()`:

```r
find_skill()               # all skills
find_skill('typescript')   # filtered by keyword
```

## Creating a new skill

Scaffold a new skill directory with a template `SKILL.md`:

```{r init_skill}
tmp <- tempfile()
init_skill('my-skill', tmp)
```

The generated `SKILL.md` looks like this:

```yaml
---
name: my-skill
description: >
  What this skill does and when to use it.
---

# My skill

Add your skill instructions here.
```

Fill in the description and instructions, then install it with `add_skill()`.

## Project vs. global skills

Each agent supports two scopes:

| Scope | Location | Use case |
|-------|----------|----------|
| `'project'` | `.agent/skills/` in the project root | Commit alongside your code; scoped to this project |
| `'global'` | `~/.agent/skills/` in the home directory | Available in every project on this machine |

```r
# Install a skill globally
add_skill('some-user/some-skill', skill_path(scope = 'global'))
```
